Automated Assessment of Residual Plots with Computer Vision Models

### 2024-11-01 paper.Rmd
keep files

```{r}
# Visual inference models and p-value calculation
# remotes::install_github("TengMCing/visage")
library(tidyverse)
library(visage)
library(glue)

>>>>

```{r}
# Visual inference models and p-value calculation
# remotes::install_github("TengMCing/visage")
options(tinytex.clean = FALSE)
library(tidyverse)
library(visage)
library(glue)
